Analysis of Bauer et al. (2023) bioRxiv: <br> Recovery completeness

### 2023-03-01 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

```{r loo}
# Leave-one-out cross validation based on posterior likelihood
loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
loo1
loo2
plot(loo1)
plot(loo2)
```

>>>>

```{r loo}
# Leave-one-out cross validation based on posterior likelihood
loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = TRUE)
loo1
loo2
plot1 <- plot(loo1)
plot2 <- plot(loo2)
plot1 / plot2
```
